A Mechanised Library for Generic (Co)Programming

### 2024-02-22 paper/paper.tex
QSort & MSort with nice extraction

Algebras on container extensions are defined as expected. The carrier of the
algebra is \mintinline{Coq}{A}, and the operations of the algebra are
morphisms of the following type:
\begin{minted}{Coq}
Notation Alg F A := (App F A ~> A).
\end{minted}

There are \emph{two} initial algebras that are, as expected, unique up to
isomorphism. We show one such initial algebra here, and the second in the
following subsection, plus a proof that they are isomorphic:

\begin{minted}{Coq}
Inductive LFix  : Type := LFix_in { LFix_out : App F LFix }.
\end{minted}
This is why we could not define equality of container extensions generically:
the contained types may not have (yet) an associated equivalence. We could have
overcame this circularity by defining simultaneously LFix and its associated
equivalence relation. But that would complicate definitions unnecessarily.
\dcas{I know ... I need to rewrite/expand on this}

>>>>

Algebras on container extensions are defined as expected. The carrier of the
algebra is \mintinline{Coq}{A}, and the operations of the algebra are morphisms
of the following type:
\begin{minted}{Coq}
Notation Alg F A := (App F A ~> A).
\end{minted}
We define \emph{two} initial algebras that are, as expected, unique up to
isomorphism. We show one such initial algebra here, and the second in the
following subsection, plus a proof that they are isomorphic:
\begin{minted}{Coq}
Inductive LFix  : Type := LFix_in { LFix_out : App F LFix }.
\end{minted}
This definition highlights why we cannot define equality of the positions and
the contained elements generically:
the contained types may not have (yet) an associated equivalence. In other
words, \mintinline{Coq}{LFix} may  We could have
overcame this circularity by defining simultaneously LFix and its associated
equivalence relation. But that would complicate definitions unnecessarily.
\dcas{I know ... I need to rewrite/expand on this}
